Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2022-09-01 ba_resubmit/response_to_reviewers.tex

	\title{Response to Reviewer Comments}

	\maketitle
	We thank the Editor and reviewers for their encouraging assessment and constructive 
	feedback.

	\section*{Editor}

	\pointRaised{%
	The paper has been reviewed by a referee and an associate editor and I have read the manuscript independently, before looking at the reports.  When I confront my notes and overall impression with the reviewers’ comments, I find myself in substantial agreement with the reviewers.

	As indicated by both reviewers, the work expands on previous work by Sadinle, introducing computational advances that are achieved by relaxing some requirements in the original formulation of the problem.  The close connections with the previous work and the extent of the novel contributions are not adequately explained.  This makes it hard for the reader to understand what is new and why the new contributions are valuable.  A careful editing of the presentation is needed to address this shortcoming.}

			\reply{E}{%
	\textbf{We thank the Editor, the AE, and the reviewer for their feedback, and pointing out our strengths of the paper and areas that we can improve the quality of our paper. In summary, we have revised our paper in the abstract and introduction as to make our contributions more clear to that of prior work.  Furthermore, we have carefully edited the paper to address issues that were pointed out by the Editorial Board.} \todo
	}

	\newpage

	\pointRaised{%
	Regarding the presentation, the AE points out a number of problems with notation, typos, and various inconsistencies.  Independently, I found many similar problems.  The intersection between what I found and what the AE found is non-empty and so is the symmetric difference.  Also, the AE found some issues that I did not find and vice versa.  So, I am almost certain that an additional review would uncover more problems.  Now, the results presented in the paper seem plausible as do the broad strokes of the derivations, but I must admit that I was not able to follow all the details. This, in large part, was because of the issues that I just mentioned, and I believe that most readers would find it difficult to follow the developments, as these issues are exceedingly distracting.

	\begin{enumerate}
	\item There are problems with the notation, which in places is not defined, in others is used before being defined, and in others yet is used inconsistently.  
	\item For example, $I_obs()$ is never defined, $n_12(Z)$ first appears on p. 5, but is not defined (in passing) until the bottom of p. 7, and it seems to become D on p. 8.  
	\item Throughout the manuscript, $n_1$ and $n_2$ are used interchangeably with $n_A$ and $n_B$, sometimes in the same section, as it happens, for example, in Section 3.1.  
	\item The loss function on p. 9 is out of Sadinle’s paper and it inherits the typo therein $(\theta_11, if Z_j, \hat{Z_j}, …)$. 
	\item  In the statement of Lemma 1 on p.13, B comes out of nowhere.  (Thinking I had missed something, I went back to the previous pages only to find out that B would be then defined in the proof.)  
	\item Formatting of all displayed math must be checked and fixed, especially as far as punctuation is concerned, as commas seem to be missing in multiple places.  
	\item For example, in Equation (1), there should be a comma after 0 and after 1, and this is by no means an isolated occurrence.
	\end{enumerate}
	}

		\reply{E}{%
	\textbf{We thank the Editor, the AE, and the reviewer for their feedback. We have made an effort to make it more clear our contributions in this work as opposed to previous work. Furthermore, we have carefully edited the paper to address issues that were pointed out by the Editorial Board.} \todo
	}

		\pointRaised{%
	Confusion can also arise from lack of clarity in the exposition.  Take comment 4 from the AE, for example.  Whose marriage certificates and whose birth records are involved?  What records are in $X_1$ and what records are in $X_2$?  The reader should not be expected to go back to Newcombe’s paper to clarify the issue. 
	}
	\reply{E}{%
	Go fix this! \todo
	}

		\pointRaised{%

		Other comments that were raised are as follows:

	\begin{enumerate}

	\item This is not an exhaustive list, but only a set of examples meant to point out what makes the paper hard to read and how it can be improved.  Many more specific points are raised in the AE’s report and here are a couple of other minor issues I noticed:

	\item p. 12, second paragraph:  insert “is” after Section 3.1

	\item p. 15:  the first sentence of the last full paragraph is either missing a verb (“we observe”?) or it includes an extra “that.”

	\item As I said, I do not believe that we, as reviewers, were able to uncover all the problems, and I strongly encourage the authors to do their part, as they should, to improve the presentation and eliminate all typos and inconsistencies.

	\item The AE finds the simulation studies to be incomplete and gives detailed suggestions on how those should be improved.  The AE also gives important suggestions about other aspects of the manuscript that must be carefully considered and addressed.  All of the AE’s comments are right on the mark.

	\end{enumerate}
	}

	\reply{E}{%
	\textbf{Go fix these!} \todo
	}

@@

	To summarize, the paper contains an interesting algorithmic contribution that can speed up calculations at the expense of relaxing some of the modeling conditions, without much adverse impact on the resulting inferences.  This aspect should be emphasized in a revised presentation.  The presentation should also make clearer the close connections to the relevant work by Sadinle, and all the issues that I mentioned above should be ironed out.

	The authors should prepare a careful and substantive revision that remains within the editorial limit of 25 pages and that answers the various comments satisfactorily.  The authors should upload the revised manuscript together with a document detailing how they addressed the reviewers’ comments.

	\reply{E}{%
		\textbf{Thank you for the opportunity to submit a revision and improve the quality of our paper. 
		We have provided detailed responses to the reviewers' comments below, 
		which prompted significant changes in our paper.}
	}

\textcolor{blue}{Suggestions/Tips for Brian to Discuss: Let's work on the easy fixes first. Go fix all the notation, check the grammar, and fix the point by point responses of the Editor as these can be done hopefully quickly. Let's use this more organized format so we can more quickly talk about what comment the Editor is making. It also makes it easier for the Editor/AE to review, so they like this (just a pointer). Suggest putting lines in the paper so we can also know where we are and it's often helpful to put changes in color so we can check every detail before resubmission. These are just some tips that have worked in the past that I hope that will help. I typically like to handle the big changes last as they take a lot of time and more attention to detail. Antidote is a nice tool for checking grammar or asking someone who is really great at proofing to find these issues and mark it up for you. Olivier is pretty good at spotting such things or Ted, so they might be good choices. Finally, given that we have some sloppy stuff going on, I'd recommend having this really polished before sending it to HRDAG or Patrick Ball will think it's a mess. I personally don't like sending things that aren't polished out the door, and this my fault for not catching this prior to submission.}

@@

	\clearpage
	\newpage

	\section*{Reviewer 2}

\textcolor{blue}{Subtle comment to Brian: The Editor told us that this review is the AE, so we want to satisfy all these comments if possible since the Editor thinks the comments are "spot on"}

	\setcounter{responsectr}{0}

	\pointRaised{%
	This manuscript addresses the bipartite matching problem in data linkage and proposes a new fast
	computation version of “Beta Linkage” to allow such matching to take place for pairs of large databases
	without resorting to ad hoc blocking. It is built upon the Felegi-Sunter model of record linkages, where
	linkages are made within strata of agreement between records across the two databases, and relies
	heavily on advances made by Sadinle (2017).
	Overall, the paper presents a practical implementation of a modified Beta Linkage approach to
	matching. It demonstrates that even though the new method suffers from the limitations of not
	seamlessly enforcing one-to-one matching, it is feasible for large datasets with modest numbers of
	features on which to match. Though the novelty of the presented methodology is primarily in the
	computational approach, I believe it to be a real advance for practical implementation of record linkage
	in modern applications.
	I have no major concerns about the content or accuracy of the presentation. However, substantial
	improvements are warranted to confirm my impression. In addition to the recommendation made by
	Reviewer 1 to include more clarity of the novel contributions of this manuscript, I believe that the
	explanation of the method should be written more clearly, the simulation comparisons should be
	repeated/expanded, and various features of the simplification should be fleshed out a bit more. Finally,
	more practical advice would be welcome. All of these points are more specifically described in the
	itemized list below
	}

	\reply{R1}{%
	\textbf{We thank the reviewer (AE) for noticing our computational novelties that expand upon the prior limitations of the prior work of Sadinle (2017). 
	Our review paper clarifies our novel contributions, improves upon the exposition of the writing, provides a practical guidance for users, and expands the simulations. We expand on these points further below.} \todo
	}

		\pointRaised{%
Overall, the notation is, somewhat by necessity, quite extensive. However, I’m not convinced that it’s entirely consistent. A glossary in the appendix may help the reader navigate the paper more easily.
            \reply{R1}{%
            \textcolor{blue}{I think this is an excellent idea and it could make sure that we don't miss anything. It would really help the reader. You could make a table of the notation, and Neil does this quite well in the Marchant 2021 paper as an example.}
            }

	}

		\pointRaised{%
Section 2, line 1: It may help to explicitly define X1 and X2 as being vectors of indices as implied
by equations (1) and (2).
}
\textcolor{red}{I'm not sure I agree with this point}
\textcolor{blue}{The reviewer is stating that equations 1 and 2 are vectorized, so everything is else needs to be vectorized as well. In short, all notation needs to be consistent.}

		\pointRaised{%
Section 2.2, beta distribution: the $n_{12}(.)$ notation needs to be defined.
}
		\reply{R1}{%
			\textbf{We thank the reviewers for identifying this oversight, and have defined the notation.}
		}

### 2022-09-02 ba_resubmit/kundinger_resubmit.tex
Worked on responses to reviewers

\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue,filecolor=blue,backref=page]{hyperref}
\usepackage{graphicx}
\newtheorem{lemma}{Lemma}
\usepackage{booktabs}       % professional-quality tables
\usepackage{algorithm}      % algorithm environment
\usepackage{algpseudocode}

@@

%% *** Frontmatter ***

\begin{frontmatter}
\title{Efficient and Scalable Bipartite Matching with Fast Beta Linkage  (fabl)}
%\title{A Sample Document\thanksref{T1}}
%\thankstext{T1}{<thanks text>}
\runtitle{Efficient and Scalable Bipartite Matching with Fast Beta Linkage  (fabl)}

@@

Recall the compact representation of the matching structure $\bm{Z} = (Z_1, Z_2, \ldots Z_{n_2})$ with $Z_j \in \{1,2, \ldots, n_1, n_1 + j\}$, where $Z_j < n_1$ indicates a link and $Z_j = n_1 + j$ indicates a nonlink. In constrast to the prior over the vector $\bm{Z}$ from \cite{sadinle_bayesian_2017}, we follow \cite{wortman2019} and use independent priors for each component $Z_j$. However, unlike \cite{wortman2019} who proposes a flat prior for $Z_j$, we propose a proper and flexible prior. We denote the fast beta prior as follows:

@@

Importantly, this independence relaxes the one-to-one requirement from \texttt{BRL}; the Gibbs sampler under \texttt{fabl} does ensure that each record in \(\bm{X}_2\) can be matched to at most one record in \(\bm{X}_1\), but allows for the possibility that multiple records in \(\bm{X}_2\) match to the same record in \(\bm{X}_1\). This behavior may be desirable; for example, we may be interested in matching birth records to marriage certificates, a situation in which such ``many-to-one'' matchings are reasonable \citep{Newcombe1963}. In situations when a bipartite estimate is desired, we can use the post processing procedure shown in section~\ref{bayes-estimate} to resolve many-to-one matchings.

@@

Since $\pi$ encodes the rate of matching across the two datasets, the posterior distribution $p(\pi|\Gamma, \bf{Z}, \Phi, \alpha_{\pi}, \beta_{\pi})$ depends only on the number of links $n_{12}(\bm{Z}) = \sum_{i=1}^{n_2}I(z_j < n_1 + 1)$ encoded by $\bm{Z}$ (and hyperparameters). Thus we use the abbreviated $p(\pi | \bf{Z}, \alpha_{\pi}, \beta_{\pi})$, and have

%As a function of \(\pi\), \(\bm{Z}\) is sequence of successes (when \(z_j < n_1 + j\)) and failures (when \(z_j = n_1 + j\)), and therefore \(p(\bm{Z}|\pi) = \mathcal{L}(\pi|\bm{Z})\) is determined only by the number of links $n_{12}(\bm{Z}) = \sum_{i=1}^{n_2}I(z_j < n_1 + 1)$ encoded by $\bm{Z}$. We have

@@

\begin{align*}
	p(\Gamma_{.j}|Z_j = z_j, \Phi) &\propto \prod_{i=1}^{n_1}\left[\prod_{f=1}^{F}\prod_{l=1}^{L_f} m_{fl}^{I(Z_j = i)}u_{fl}^{I(Z_j \neq i)}\right]^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)}\\
	&\propto \prod_{i=1}^{n_1}\left(\prod_{f=1}^{F}\prod_{l=1}^{L_f} \frac{m_{fl}}{u_{fl}}\right)^{I(z_j = i) I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)} \\
	&=
	\begin{cases} 
		w_{z_j, j}  & z_j \leq n_1; \\
		1 &  z_j  = n_1 + j \\
	\end{cases}\\
\end{align*}

where
%$w_{ij} = \left(\frac{\prod_{f=1}^{F}\prod_{l=1}^{L_f} m_{fl}}{\prod_{f=1}^{F}\prod_{l=1}^{L_f} u_{fl}}\right)^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)} = \frac{P(\boldsymbol{\gamma_{ij}}|Z_j = i)}{P(\boldsymbol{\gamma_{ij}} |Z_j \neq i)}$.
$$w_{ij} = \prod_{f=1}^{F}\prod_{l = 1}^{L_f} \left(\frac{m_{fl}}{u_{fl}}\right)^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)}.$$

@@

With the likelihood in this form, we can derive the full conditional
\begin{align*}
	p(Z_j|\Gamma_{.j}, \Phi, \pi) &\propto p(\Gamma_{.j}| Z_j, \Phi) P(Z_j|\pi) \\
	&\propto \left(\sum_{i=1}^{n_1}w_{ij}\bm{1}_{z_j = i} + \bm{1}_{z_j = n_1 + 1}\right)\left(\pi\sum_{i=1}^{n_1}\frac{1}{n_1}\bm{1}_{z_j = i} + (1-\pi)\bm{1}_{z_j = n_1 + 1}\right) \\	
	&= \frac{\pi}{n_1}\sum_{i=1}^{n_1}w_{ij}\bm{1}_{z_j = i} + (1-\pi)\bm{1}_{z_j = n_1 + 1}.
\end{align*}
Thus, we have
$$Z_j^{(s+1)} | \Phi, \Gamma, \pi \propto \begin{cases} 
	\frac{\pi}{n_1}w_{z_{j},j}   & z_j \leq n_1; \\
	1-\pi &  z_j  = n_1 + 1. \\
\end{cases}$$
We integrate over \(\pi\) and rearrange terms to produce the final full conditional:

\[p\left(Z_j^{(s+1)}  = i| \Phi, \bm{Z^{(s)}}\right) \propto
\begin{cases} 
	w_{ij}  & i \leq n_1; \\
	n_1 \frac{n_2 - n_{12}(\bm{Z}) + \beta_{\pi}}{n_{12}(\bm{Z}) + \alpha_{\pi}} & i  = n_1 + j. \\
\end{cases}\]

@@

With SEI, however, we can reduce the comparison space, and its associated storage costs, while avoiding these drawbacks. Observe that all records $i \in \bm{X}_1$ that share the same agreement pattern with $j \in \bm{x}_2$ have the same Fellegi Sunter weight $w_{ij}$, and therefore the same probability when sampling \(Z_j\). Thus, we know that records $i \in r_{j_p}$  such that $H_{j_p}$ is large are very unlikely to be sampled consistently enough to be deemed a match through the Bayes estimate. We know this regardless of the form of the agreement pattern itself, or its associated probabilities. Therefore, rather than store all of these unlikely record labels, we choose to store only a small number \(S\) of them in a new nested listed $\mathcal{R}^{\text{SEI}}$. Rather than storing \(n_1 \times n_2\) record labels, SEI allows us to store at most
\(n_2 \times P \times S\) labels, regardless of how large \(n_1\) might be. Posterior calculations still attribute the appropriate weight to all records through the summary statistics in $\mathcal{H}$, and thus we can proceed with posterior inference through the memory reduced $\tilde{\Gamma}^{\text{SEI}} = \{\mathcal{P}, \mathcal{R}^{\text{SEI}}, \mathcal{H}\}$. For simplicty, we suppress ``SEI'' in future notation, and use $\tilde{\Gamma}$ without loss of generality.

@@

	\begin{lemma}
		The overall computational complexity of \texttt{fabl} is $O(\frac{F}{B} n_1 n_2) + O(n_2 P)$, where $B$ is the number of processors available for parallelization.
		\label{lemma:fabl}
	\end{lemma}

@@

	\begin{figure}[t]
		\begin{center}
			\includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_sim_plot2} 
			\caption{Posterior means and credible intervals for accuracy metrics under the replication of simulation study from \cite{sadinle_bayesian_2017}. For each level of overlap and each level of error, we have 100 paired sets of 500 records. We see comparable performance for all levels of error and overlap.}
			\label{fig:sadinle_simulation}
		\end{center}
	\end{figure}

@@

	The National Long Term Care Study (NLTCS) is a longitudinal study tracking the health outcomes of Medicare recipients. The initial survey began in 1982, with follow-up surveys taken approximately every five years. For this study, we seek to link records over the $n_1 = 20485$ records from 1982 to the $n_2 = 17466$ records from 1989. The NLTCS data have longitudinal links, so that in reality one does not need to do a record linkage.  However, following the strategy in \cite{guha:reiter:BA} we break the longitudinal links and treat the data from 1982 and 1989 as stand-alone files.

>>>>

\usepackage{lineno}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue,filecolor=blue,backref=page]{hyperref}
\usepackage{graphicx}
\newtheorem{lemma}{Lemma}
\usepackage{booktabs}       % professional-quality tables
\usepackage{algorithm}      % algorithm environment
\usepackage{algpseudocode}

@@

%% *** Frontmatter *** 
\linenumbers
\begin{frontmatter}
\title{Efficient and Scalable Bipartite Matching with Fast Beta Linkage  (fabl)}
%\title{A Sample Document\thanksref{T1}}
%\thankstext{T1}{<thanks text>}
\runtitle{Efficient and Scalable Bipartite Matching with Fast Beta Linkage  (fabl)}

@@

Recall the compact representation of the matching structure $\bm{Z} = (Z_1, Z_2, \ldots Z_{n_2})$ with $Z_j \in \{1,2, \ldots, n_1, n_1 + j\}$, where $Z_j < n_1$ indicates a link and $Z_j = n_1 + j$ indicates a nonlink. In contrast to the prior over the vector $\bm{Z}$ from \cite{sadinle_bayesian_2017}, we follow \cite{wortman2019} and use independent priors for each component $Z_j$. However, unlike \cite{wortman2019} who proposes a flat prior for $Z_j$, we propose a proper and flexible prior. We denote the fast beta prior as follows:

@@

Importantly, this independence relaxes the one-to-one requirement from \texttt{BRL}; the Gibbs sampler under \texttt{fabl} does ensure that each record in \(\bm{X}_2\) can be matched to at most one record in \(\bm{X}_1\), but allows for the possibility that multiple records in \(\bm{X}_2\) match to the same record in \(\bm{X}_1\). To resolve many-to-one matchings and obtain a one-to-one estimate, we use the post processing procedure shown in section~\ref{bayes-estimate}.

Lastly, we note that it is common to encounter missing information in datasets used for record linkage. Whether information is missing in record $i \in \bf{X}_1$ or $j \in \bf{X}_2$, the comparison vector $\bf{\gamma}_{ij}$ will have missing values. We handle this issue by assuming that this missingness occurs at random (MAR, by \cite{LittleRubin2002})

@@

Since $\pi$ encodes the rate of matching across the two datasets, the posterior distribution $p(\pi|\Gamma, \bf{Z}, \Phi, \alpha_{\pi}, \beta_{\pi})$ depends only on the number of links $n_{12}(\bm{Z}) = \sum_{i=1}^{n_2}I(z_j < n_1 + j)$ encoded by $\bm{Z}$ (and hyperparameters). Thus we use the abbreviated $p(\pi | \bf{Z}, \alpha_{\pi}, \beta_{\pi})$, and have

%As a function of \(\pi\), \(\bm{Z}\) is sequence of successes (when \(z_j < n_1 + j\)) and failures (when \(z_j = n_1 + j\)), and therefore \(p(\bm{Z}|\pi) = \mathcal{L}(\pi|\bm{Z})\) is determined only by the number of links $n_{12}(\bm{Z}) = \sum_{i=1}^{n_2}I(z_j < n_1 + j)$ encoded by $\bm{Z}$. We have

@@

\textcolor{red}{I added the second line, showing the division by all the u's. Its pretty ugly! What do you guys think?}

\begin{align*}
	p(\Gamma_{.j}|Z_j = z_j, \Phi) &\propto \prod_{i=1}^{n_1}\left[\prod_{f=1}^{F}\prod_{l=1}^{L_f} m_{fl}^{I(Z_j = i)}u_{fl}^{I(Z_j \neq i)}\right]^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)}\\
	&\propto \prod_{i=1}^{n_1}\frac{\left[\prod_{f=1}^{F}\prod_{l=1}^{L_f} m_{fl}^{I(Z_j = i)}u_{fl}^{I(Z_j \neq i)}\right]^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)}}{\prod_{f=1}^{F}\prod_{l=1}^{L_f} u_{fl}^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)}}\\
	&\propto \prod_{i=1}^{n_1}\left(\prod_{f=1}^{F}\prod_{l=1}^{L_f} \frac{m_{fl}}{u_{fl}}\right)^{I(z_j = i) I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)} \\
	&=
	\begin{cases} 
		w_{z_j, j}  & z_j \leq n_1; \\
		1 &  z_j  = n_1 + j \\
	\end{cases}\\
\end{align*}

where
$$w_{ij} = \prod_{f=1}^{F}\prod_{l = 1}^{L_f} \left(\frac{m_{fl}}{u_{fl}}\right)^{I(\gamma_{ij}^f = l)I_{obs}(\gamma_{ij}^f)}.$$

@@

With the likelihood in this form, we can derive the full conditional
\begin{align*}
	p(Z_j|\Gamma_{.j}, \Phi, \pi) &\propto p(\Gamma_{.j}| Z_j, \Phi) P(Z_j|\pi) \\
	&\propto \left(\sum_{i=1}^{n_1}w_{z_j, j}I(z_j = i) + I(z_j = n_1 + j) \right) \left (\pi\sum_{i=1}^{n_1}\frac{1}{n_1}I(z_j = i) + (1-\pi)I(z_j = n_1 + j) \right) \\	
	&= \frac{\pi}{n_1}\sum_{i=1}^{n_1}w_{z_j, j}I(z_j = i) + (1-\pi)I(z_j = n_1 + j).
\end{align*}
Thus, we have
$$Z_j^{(s+1)} | \Phi, \Gamma, \pi \propto \begin{cases} 
	\frac{\pi}{n_1}w_{z_{j}, j}   & z_j \leq n_1; \\
	1-\pi &  z_j  = n_1 + j. \\
\end{cases}$$
We integrate over \(\pi\) and rearrange terms to produce the final full conditional:

\textcolor{red}{This is the derivation for integrating out $\pi$. Should it go here, or in the appendix?}
\begin{align*}
	\int_{\pi}p(Z_j | \Phi, \Gamma, \pi) d\pi &= \int_{\pi}\left[\frac{\pi}{n_1}w_{z_{j}, j} I(z_j\leq n_1) + (1-\pi)I(z_j = n_1 + j)\right]d\pi \\
	&= \frac{\int_{\pi} \pi d\pi}{n_1}w_{z_{j}, j} I(z_j\leq n_1) + \left(1-\int_{\pi} \pi d\pi \right) I(z_j = n_1 + j) \\
	&= \frac{n_{12}(\bf{Z}) + \alpha_{\pi}}{n_1 (n_2 + \alpha_{\pi} + \beta_{\pi})}w_{z_{j}, j} I(z_j\leq n_1) + \frac{n_2 - n_{12}(\bf{Z}) + \beta_{\pi}}{n_2 + \alpha_{\pi} + \beta_{\pi}}I(z_j = n_1 + j) \\
	&\propto w_{z_j, j}I(z_j\leq n_1) + n_1 \frac{n_2 - n_{12}(\bm{Z}) + \beta_{\pi}}{n_{12}(\bm{Z}) + \alpha_{\pi}}I(z_j = n_1 + j) \\
	&\propto 
	\begin{cases} 
		w_{z_j, j}  & z_j \leq n_1; \\
		n_1 \frac{n_2 - n_{12}(\bm{Z}) + \beta_{\pi}}{n_{12}(\bm{Z}) + \alpha_{\pi}} & z_j   = n_1 + j. \\
	\end{cases} \\
\end{align*}

\[p\left(Z_j^{(s+1)}  = i| \Phi, \bm{Z^{(s)}}\right) \propto
\begin{cases} 
	w_{z_j, j}  & z_j \leq n_1; \\
	n_1 \frac{n_2 - n_{12}(\bm{Z}) + \beta_{\pi}}{n_{12}(\bm{Z}) + \alpha_{\pi}} & z_j   = n_1 + j. \\
\end{cases}\]

@@

With SEI, however, we can reduce the comparison space, and its associated storage costs, while avoiding these drawbacks. Observe that all records $i \in \bm{X}_1$ that share the same agreement pattern with $j \in \bm{X}_2$ have the same Fellegi Sunter weight $w_{ij}$, and therefore the same probability when sampling \(Z_j\). Thus, we know that records $i \in r_{j_p}$  such that $H_{j_p}$ is large are very unlikely to be sampled consistently enough to be deemed a match through the Bayes estimate. We know this regardless of the form of the agreement pattern itself, or its associated probabilities. Therefore, rather than store all of these unlikely record labels, we choose to store only a small number \(S\) of them in a new nested listed $\mathcal{R}^{\text{SEI}}$. Rather than storing \(n_1 \times n_2\) record labels, SEI allows us to store at most
\(n_2 \times P \times S\) labels, regardless of how large \(n_1\) might be. \textcolor{red}{In practice, we recommend $S=10$, as this reduces the number of stored indices for highly unlikely record pairings, but does is not likely to eliminate any of the indices for likely matches. Choosing $S$ too low can concentrate undue mass on unlikely matches and distort linkage results.}Posterior calculations still attribute the appropriate weight to all records through the summary statistics in $\mathcal{H}$, and thus we can proceed with posterior inference through the memory reduced $\tilde{\Gamma}^{\text{SEI}} = \{\mathcal{P}, \mathcal{R}^{\text{SEI}}, \mathcal{H}\}$. For simplicity, we suppress ``SEI'' in future notation, and use $\tilde{\Gamma}$ without loss of generality.

@@

	\begin{lemma}
		Recall that $n_1$ and $n_2$ are the number of records in $\bf{X}_1$ and $\bf{X}_2$ respectively, $F$ is the number of fields used for comparisons across records, and $P$ is the number of patterns that comparison vectors can exhibit. We assume $B$ processors available for parallelization. Then, the overall computational complexity of \texttt{fabl} is $O(\frac{F}{B} n_1 n_2) + O(n_2 P)$.
		\label{lemma:fabl}
	\end{lemma}

@@

	\begin{figure}[t]
		\begin{center}
			\includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_sim_plot2} 
			\caption{Posterior means and credible intervals for accuracy metrics under the replication of simulation study from \cite{sadinle_bayesian_2017}. For each level of overlap and each level of error, we have 100 paired sets of 500 records. Thus this table represents results for 900 datasets. We see comparable performance for all levels of error and overlap.}
			\label{fig:sadinle_simulation}
		\end{center}
	\end{figure}

@@

	The National Long Term Care Study (NLTCS) is a longitudinal study tracking the health outcomes of Medicare recipients. The initial survey began in 1982, with follow-up surveys taken approximately every five years. For this study, we seek to link records over the $n_1 = 20485$ records from 1982 to the $n_2 = 17466$ records from 1989. \textcolor{red}{In each iteration of the study, some participants are added to the lists, and others are lost due to loss of contact or death.} The NLTCS data have longitudinal links, so that in reality one does not need to conduct record linkage.  However, following the strategy in \cite{guha:reiter:BA} we break the longitudinal links and treat the data from 1982 and 1989 as stand-alone files.
